\documentclass[12pt, a4paper]{article}

% ── Packages ──────────────────────────────────────────────────────────────────
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=2.4cm, top=2.8cm, bottom=2.8cm]{geometry}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{xcolor}
\usepackage{mdframed}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{array}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{hyperref}

% ── Colors ────────────────────────────────────────────────────────────────────
\definecolor{accent}{RGB}{94, 106, 210}       % indigo
\definecolor{lightgray}{RGB}{245, 246, 248}
\definecolor{darkgray}{RGB}{60, 65, 80}
\definecolor{mutedtext}{RGB}{110, 115, 130}
\definecolor{green}{RGB}{22, 163, 74}
\definecolor{amber}{RGB}{180, 120, 20}

% ── Hyperref ──────────────────────────────────────────────────────────────────
\hypersetup{
  colorlinks=true,
  linkcolor=accent,
  urlcolor=accent,
  pdfauthor={dedomena},
  pdftitle={dedomena -- Product Overview},
}

% ── Section styles ────────────────────────────────────────────────────────────
\titleformat{\section}
  {\large\bfseries\color{darkgray}}
  {}
  {0em}
  {}
  [\vspace{-0.3em}\textcolor{accent}{\rule{\linewidth}{1.5pt}}\vspace{0.4em}]

\titleformat{\subsection}
  {\normalsize\bfseries\color{darkgray}}
  {}
  {0em}
  {}

\titlespacing{\section}{0pt}{1.8em}{0.6em}
\titlespacing{\subsection}{0pt}{1.2em}{0.3em}

% ── Header and footer ─────────────────────────────────────────────────────────
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\textcolor{mutedtext}{dedomena \textsigma}}
\fancyhead[R]{\small\textcolor{mutedtext}{Product Overview}}
\fancyfoot[C]{\small\textcolor{mutedtext}{\thepage}}
\renewcommand{\headrulewidth}{0pt}

% ── Callout box ───────────────────────────────────────────────────────────────
\newmdenv[
  backgroundcolor=lightgray,
  linecolor=accent,
  linewidth=3pt,
  topline=false,
  bottomline=false,
  rightline=false,
  innerleftmargin=14pt,
  innerrightmargin=14pt,
  innertopmargin=10pt,
  innerbottommargin=10pt,
  skipabove=10pt,
  skipbelow=10pt,
]{callout}

% ── Highlight box ─────────────────────────────────────────────────────────────
\newmdenv[
  backgroundcolor=accent!8,
  linecolor=accent!40,
  linewidth=1pt,
  roundcorner=4pt,
  innerleftmargin=14pt,
  innerrightmargin=14pt,
  innertopmargin=10pt,
  innerbottommargin=10pt,
  skipabove=10pt,
  skipbelow=10pt,
]{highlight}

% ── Document ──────────────────────────────────────────────────────────────────
\begin{document}

% ── Cover block ───────────────────────────────────────────────────────────────
\begin{center}
  \vspace*{1.2cm}
  {\fontsize{32}{38}\selectfont\bfseries\color{darkgray} dedomena}
  \hspace{0.4em}
  {\fontsize{32}{38}\selectfont\color{accent!50} \textsigma}

  \vspace{0.5em}
  {\large\color{mutedtext} A smarter way to work with your data}

  \vspace{1.4em}
  \textcolor{accent!30}{\rule{6cm}{0.6pt}}

  \vspace{1em}
  {\small\color{mutedtext}
    Product Overview \quad\textbullet\quad Internal Document \quad\textbullet\quad \today
  }
  \vspace{1.6cm}
\end{center}

% ── 1. What is dedomena ───────────────────────────────────────────────────────
\section{What Is dedomena?}

dedomena is a web-based platform that lets anyone in the organisation ask questions
about business data in plain English and get clear, sourced answers in seconds.

No SQL. No Excel formulas. No waiting for an analyst to run a report.
You connect your data sources once, type your question, and the platform does the rest.

\begin{callout}
  \textbf{Think of it like having a very knowledgeable assistant who has read every
  spreadsheet, every database table, and every report in the company, and who is always
  ready to answer a question instantly.}
\end{callout}

% ── 2. The problem we are solving ─────────────────────────────────────────────
\section{The Problem We Are Solving}

Right now, getting answers from data at our organisation looks like this:

\begin{enumerate}[leftmargin=1.6em, itemsep=4pt]
  \item A manager or team lead needs a number or a summary.
  \item They email an analyst or open a ticket.
  \item The analyst has to find the right data source, write a query or formula,
        and format a report.
  \item The answer arrives hours or days later.
  \item By the time it does, the context has shifted.
\end{enumerate}

This process is slow, it creates a bottleneck on a small number of technical people,
and it means decisions are made without the information that already exists.

Beyond speed, there is a second problem: \textbf{data lives in too many places at once}.
CRM records are in one tool. Financial data is in another. Project updates live in
spreadsheets. Nobody has a single view of all of it.

% ── 3. How we will use dedomena ───────────────────────────────────────────────
\section{How We Will Use dedomena}

\subsection{Step one: Connect our data sources}

We start by connecting the tools and databases we already use. This is a one-time
setup that takes a few minutes per source. dedomena supports more than one hundred
common business tools out of the box, including:

\vspace{0.5em}
\begin{tabular}{>{\color{mutedtext}\small}p{4.5cm} >{\small}p{9cm}}
  \toprule
  \textbf{\normalcolor Category} & \textbf{Examples we can connect} \\
  \midrule
  CRM and sales       & Salesforce, HubSpot, Pipedrive \\
  Databases           & PostgreSQL, MySQL, BigQuery, Snowflake \\
  Spreadsheets and files & Excel, CSV, PDF, Google Sheets \\
  Cloud storage       & Google Drive, OneDrive, SharePoint, Dropbox \\
  Finance             & QuickBooks, Stripe, accounting exports \\
  Project management  & Notion, Airtable, Jira, Asana \\
  Communication       & Slack exports, email archives \\
  \bottomrule
\end{tabular}

\vspace{0.8em}
Once connected, dedomena reads the data and keeps it ready for questions.
Nothing is uploaded to a third party. Everything stays within our environment.

\subsection{Step two: Ask questions}

Any team member with access to the platform can open dedomena, type a question,
and receive an answer. The question can be anything that relates to the connected data.

\vspace{0.4em}
Here are realistic examples of what we would actually type:

\begin{highlight}
  \textit{"What were our top five accounts by revenue last quarter?"}

  \vspace{0.4em}
  \textit{"Show me a summary of all open support tickets created this month."}

  \vspace{0.4em}
  \textit{"Which product line has the highest return rate according to our sales data?"}

  \vspace{0.4em}
  \textit{"Compare our headcount from January to today and flag any departments that grew by more than 20 percent."}
\end{highlight}

\vspace{0.4em}
dedomena reads across all connected sources at once, finds the relevant information,
and writes a clear answer with references to where the data came from.

\subsection{Step three: Act on the results}

The platform does not just return a number. It explains what it found, flags
anything that looks unusual, and can present the information as a summary,
a table, or a list, depending on what is most useful.

This gives the person asking the question everything they need to make a decision
or take action, without needing to open a single spreadsheet.

% ── 4. Who benefits and how ───────────────────────────────────────────────────
\section{Who Benefits and How}

\begin{tabular}{>{\bfseries\color{darkgray}}p{3.5cm} p{10.5cm}}
  \toprule
  \textbf{Role} & \textbf{What changes for them} \\
  \midrule
  Managers and directors
  &
  They get answers to operational questions in under a minute instead of waiting
  for a report. They can monitor performance, compare periods, and spot trends
  without involving the data team. \\[8pt]

  Sales and account teams
  &
  They can pull up customer history, deal status, and account health instantly,
  directly from the CRM and financial data, without needing a dashboard that
  someone else built. \\[8pt]

  Operations teams
  &
  They can query inventory levels, supplier data, and process metrics across
  multiple systems at once and get a combined view in one place. \\[8pt]

  Finance teams
  &
  They can cross-reference accounting exports with other business data and ask
  questions like \textit{"which cost centres are over budget this quarter?"} without
  writing a single formula. \\[8pt]

  Analysts and developers
  &
  They stop being the first point of contact for every data question. They can
  focus on deeper work while the rest of the organisation handles routine queries
  independently. \\
  \bottomrule
\end{tabular}

% ── 5. What makes it different ────────────────────────────────────────────────
\section{What Makes It Different from Other Tools}

\subsection{It understands questions, not just keywords}

Most search tools and dashboards require you to know exactly what you are looking
for and where it is stored. dedomena understands the meaning of a question and
figures out which data is relevant on its own. You do not need to know which database
table holds the answer.

\subsection{It works across multiple sources at once}

A standard BI tool answers questions about one dataset at a time. dedomena can read
from five different connected sources simultaneously and combine them into a single
answer. If the answer requires data from both the CRM and the finance system,
it finds it in both and gives you one coherent response.

\subsection{The data stays with us}

This is important from a compliance standpoint. dedomena does not upload your raw
data to any external server. When a question is asked, only the portions of the
data that are relevant to that specific question are sent to the AI to generate the
answer. The rest stays in place.

\subsection{No training or technical knowledge required}

Any member of the team can use it from day one. There is no query language to learn,
no dashboard to configure, and no report template to fill in. If you can type a
question in plain English, you can use dedomena.

% ── 6. What we get as an organisation ────────────────────────────────────────
\section{What We Get as an Organisation}

\begin{enumerate}[leftmargin=1.6em, itemsep=8pt]

  \item \textbf{Faster decision-making.}
  Questions that used to take days to answer take seconds.
  Teams can act on information while it is still relevant.

  \item \textbf{Less dependency on technical staff for routine questions.}
  Analysts and developers are freed from handling basic data requests.
  They spend their time on work that actually requires their skills.

  \item \textbf{One place to ask questions about all of our data.}
  Instead of logging into five different tools and exporting five spreadsheets,
  everyone queries through one interface.

  \item \textbf{A full record of what was asked and when.}
  Every question is logged with the sources it used.
  This creates a natural audit trail for any data-driven decision.

  \item \textbf{Better data literacy across the organisation.}
  When people can ask questions directly, they engage with data more often.
  Over time, this builds a culture where decisions are grounded in evidence.

\end{enumerate}

% ── 7. Rollout plan ───────────────────────────────────────────────────────────
\section{Suggested Rollout Plan}

\begin{tabular}{>{\bfseries\color{darkgray}}p{2.5cm} p{11.5cm}}
  \toprule
  \textbf{Phase} & \textbf{What happens} \\
  \midrule
  Phase 1
  &
  Connect two or three of our most-used data sources. Run a two-week pilot with
  a small group of managers and team leads. Gather feedback on which questions
  they ask most often and whether the answers are accurate and useful. \\[8pt]

  Phase 2
  &
  Expand to the full list of data sources. Open access to all teams.
  Run a short onboarding session so that everyone knows how to ask a well-formed
  question and how to interpret the answers. \\[8pt]

  Phase 3
  &
  Use the query history to identify the most common information needs across the
  organisation. Build standing summaries or scheduled reports for those use cases
  so that key information is always ready without anyone needing to ask. \\
  \bottomrule
\end{tabular}

% ── 8. Summary ────────────────────────────────────────────────────────────────
\section{Summary}

dedomena gives our organisation the ability to ask any question about our data and
get a clear, reliable answer in seconds, without writing code, without waiting for
a report, and without needing to know where the data lives.

We will use it to reduce the time between a question and a decision, to remove the
bottleneck that currently sits on our analytics team, and to give every member of
the team direct access to the information they need to do their job well.

\begin{callout}
  \textbf{The goal is simple:} anyone in the organisation should be able to open
  dedomena, type a question about our business, and have a clear answer in front
  of them before their coffee gets cold.
\end{callout}

\vspace{2em}
\textcolor{mutedtext}{\small This document is intended for internal review. For a live demonstration
or to discuss integration with our existing tools, please reach out to the product team.}

\end{document}
